First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-13 eg6-letters/coherent/dvcs_he4_prl.tex
more writting corrections

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of Deeply Virtual Compton 
Scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer (CLAS). A new 
radial time projection chamber (RTPC) was used to detect the recoiling $^4$He 
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries (BSA) are significantly larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, the chiral even Generalized 
Parton Distribution (GPD) $H_{A}$ of $^4$He. This pioneering measurement leads 
the way toward the 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

The most promising way to access GPDs experimentally is through the measurement 
of deep virtual Compton scattering (DVCS), i.e.  the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN.  The vast majority of these measurements focused on the study of proton 
structure and allowed extraction of the tomography of the nucleon (for details 
on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

>>>>

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of Deeply Virtual Compton 
Scattering (DVCS) off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from CEBAF machine at Jefferson Lab projected onto a $^4$He gas 
target in the center of the CEBAF Large Acceptance Spectrometer (CLAS). A new 
Radial Time Projection Chamber (RTPC) was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured Beam Spin 
Asymmetries (BSA) are significantly larger than that observed on the proton in 
the same kinematic domain. Since $^4$He is a spin zero target, we were able to 
extract, in a completely model independent way, the chiral even Generalized 
Parton Distribution (GPD) $H_{A}$ of $^4$He. This pioneering measurement leads 
the way toward the 3D imaging of the partonic structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

The most promising way to access GPDs experimentally is through the measurement 
of Deep Virtual Compton Scattering (DVCS), i.e.  the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab (JLab), HERA and  
CERN.  The vast majority of these measurements focused on the study of proton 
structure and allowed extraction of the tomography of the nucleon (for details 
on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.
